Democratizing Secure Two-Party Computation

### 2017-10-16 OaklandSubmission/intro.tex
minor fix

Suppose a developer wants to compute $w^Tx >0$ securely using
SMC. With the current techniques, he has two options.\aseem{Nice
  first example.} \aseem{We should
  use she for the programmer instead of he?}
\begin{tiret}
\item He can code up the functionality in a programmer friendly
  domain-specific language such as
  \cite{lambdaps,wysteria,oblivm,smcl} that would automatically
  compile it to an SMC protocol. The downside is that all of these
  works build on a cryptographic back-end that is either entirely
  boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}\aseem{This
    homo citation is broken.}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
\item To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of
complex trade-offs between arithmetic and boolean cryptographic
schemes and split the functionality into such parts accordingly. In
their framework, the programmer is required to write circuits
consisting of  arithmetic and boolean gates along with appropriate
conversion gates. In short, the current system of ABY is not suitable
to be used by non-specialist programmers.\aseem{Doesn't their paper
  itself say that the framework is not programmable and we need
  a high-level language and a compiler for mixed protocols?}

@@

In this work, we develop and implement our framework \tool \nc{I still
  like EasyPC :)} \divya{I agree that \tool is bad. What would be the
  full form for EasyPC? Shouldn't it be EasySC?} for secure
computation that achieves generality, performance and programmer
productivity. The programmer writes a high level \divya{C-like}
program (instead of a circuit) to describe the function to be
computed. Our compiler automatically generates an SMC protocol using a
mix of Arithmetic and Boolean compute. Our compiler is general and can
work with any secure implementation of a mix of arithmetic and boolean
computations. In our work, we focus on semi-honest secure two-party
computation. We build on ABY \cite{aby} that provides the suitable
cryptographic back-end in this setting. We provide a formal type
system and prove correctness and security of our compiler. We evaluate
our system on various benchmarks such as logistic regression and
convolutional neural network (CNN) for MNIST data \cite{minionn},
naive bayes, decision trees from \cite{shafindss}. Evaluations show
that protocols generated by our compiler match (\aseem{or better?})
the performance of hand-crafted protocols in most cases (see
\sectionref{eval}). Below, we will  give an overview of \tool and
describe our contributions in more detail.

>>>>

Suppose a developer wants to compute $w^Tx >b$ securely using
SMC. With the current techniques, he has two options.\aseem{Nice
  first example.} \aseem{We should
  use she for the programmer instead of he?}
\begin{tiret}
\item He can code up the functionality in a programmer friendly
  domain-specific language such as
  \cite{lambdaps,wysteria,oblivm,smcl} that would automatically
  compile it to an SMC protocol. The downside is that all of these
  works build on a cryptographic back-end that is either entirely
  boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}\aseem{This
    homo citation is broken.}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
\item To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of
complex trade-offs between arithmetic and boolean cryptographic
schemes and split the functionality into such parts accordingly. In
their framework, the programmer is required to write circuits
consisting of  arithmetic and boolean gates along with appropriate
conversion gates. In short, the current system of ABY is not suitable
to be used by non-specialist programmers.\aseem{Doesn't their paper
  itself say that the framework is not programmable and we need
  a high-level language and a compiler for mixed protocols?}

@@

In this work, we develop and implement our framework \tool \nc{I still
  like EasyPC :)} \divya{I agree that \tool is bad. What would be the
  full form for EasyPC? Shouldn't it be EasySC?} for secure
computation that achieves generality, performance and programmer
productivity. The programmer writes a high level \divya{C-like}
program (instead of a circuit) to describe the function to be
computed. Our compiler automatically generates an SMC protocol using a
mix of Arithmetic and Boolean compute. Our compiler is general and can
work with any secure implementation of a mix of arithmetic and boolean
computations. In our work, we focus on semi-honest secure two-party
computation. We build on ABY \cite{aby} that provides the suitable
cryptographic back-end in this setting. We provide a formal type
system and prove correctness and security of our compiler. We evaluate
our system on various benchmarks such as logistic regression and
convolutional neural network (CNN) for MNIST data \cite{minionn},
naive bayes, decision trees from \cite{shafindss}. Evaluations show
that protocols generated by our compiler match
the performance or outperform hand-crafted protocols in most cases (see
\sectionref{eval}). Below, we will  give an overview of \tool and
describe our contributions in more detail.
